SSwAB-IT Phase 1 Analysis

### 2024-03-08 Jordana Hoppe/SSwAB-IT/phase_1_analysis.qmd

---
title: "SSwAB-IT Phase 1 Analysis"
author: "Tim Vigers"
date: "today"
date-format: long
format:
  html:
    toc: true
    toc-depth: 5
    toc-float: true
    code-fold: true
    self-contained: true
    fig-cap-location: top
    page-layout: full
    theme:
      light: flatly
      dark: darkly
bibliography: /Volumes/Documents/Miscellaneous/zotero.bib
csl: /Volumes/Documents/Miscellaneous/american-medical-association.csl
editor: source
---

```{r setup}
#| include: false
library(tidyverse)
library(gtsummary)
library(redcapAPI)
library(irr)
library(knitr)
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF",
  "Windows" = "C:/Users/timvigers/OneDrive - The University of Colorado Denver/Vigers/CF"
)
knitr::opts_knit$set(root.dir = home_dir)
```

@@

```{r results='asis'}
invisible(lapply(names(bug_list), function(b) {
  cat("\n")
  cat("##", as.character(bug_list[b]))
  cat("\n")
  cos <- paste0(b, "_cos")
  sos <- paste0(b, "_sos")
  d <- df[, c(cos, sos)]
  d <- d[complete.cases(d), ]
  t <- data.frame(table(d))
  colnames(t) <- c("COS", "SOS", "n")
  cat("\n")
  print(kable(t))
  cat("\n")
}))
```

>>>>

---
title: "SSwAB-IT Phase 1 Analysis"
author: "Tim Vigers"
date: "today"
date-format: long
format:
  html:
    toc: true
    toc-depth: 5
    toc-float: true
    code-fold: true
    self-contained: true
    fig-cap-location: top
    page-layout: full
    theme:
      light: flatly
      dark: darkly

editor: source
---

```{r setup}
#| include: false
library(tidyverse)
library(gtsummary)
library(redcapAPI)
library(irr)
library(knitr)
library(caret)
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF",
  "Windows" = "C:/Users/timvigers/OneDrive - The University of Colorado Denver/Vigers/CF"
)
knitr::opts_knit$set(root.dir = home_dir)
```

@@

```{r results='asis'}
invisible(lapply(names(bug_list), function(b) {
  cat("\n")
  cat("##", as.character(bug_list[b]))
  cat("\n")
  cos <- paste0(b, "_cos")
  sos <- paste0(b, "_sos")
  d <- df[, c(cos, sos)]
  d <- d[complete.cases(d), ]
  t <- data.frame(table(d))
  colnames(t) <- c("COS", "SOS", "n")
  cat("\n")
  print(kable(t))
  cat("\n")
  cat("\n")
  c <- confusionMatrix(d[, sos], reference = d[, cos], mode = "everything")
  cat("### 2x2 table")
  print(kable(c$table))
  cat("\n")
  cat("\n")
  cat("#### 2x2 table metrics")
  print(kable(c$byClass))
  cat("\n")
}))
```
